Sea level

### 2016-12-07 EU-Circle/eu-circle_case-study-SL.Rmd

---
title: "CixPAG - spells"
author: "Rasmus Benestad"
date: "November 3, 2016"
output: pdf_document
---

@@

@@

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

@@

```{r pressure, echo=FALSE}
plot(pressure)
```

@@

Scatter plots: mean versus standard deviation of anomalies. 
Combine several stations to link mean with mean spell length?

Downscaling of heat wave spell length. Paper. Wheat.

>>>>

---
title: "Sea level"
author: "Rasmus Benestad"
date: "December 7, 2016"
output: pdf_document
---

@@

Evidence for coherent the local sea level rise based on PCA. Relate the local response to the global, expecting a physical connection

@@

```{r esd}
library(esd)
library(RgoogleMaps)
```

## Analysis

@@

```{r sea-level-data}
gsl <- GSL()
gloss <- station.gcloss()
sonel <- station.sonel()
newlin <- station.newlin()
```

@@
